Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-18 workflow/workflow.Rmd
try plot with ercc

```{r parallel}
NCORES <- 6
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing on your computer.")
  register(SerialParam())
}
```

@@

>>>>

```{r parallel}
NCORES <- 2
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing on your computer.")
  register(SerialParam())
}
```

@@

```{r}
# added chunk of code
library(scater)
sce <- calculateQCMetrics(
    dataObj,
    feature_controls = list(
        ERCC = isSpike(sce, "ERCC")
    )
)
cData <- colData(sce)
cData <- as.data.frame(cData)
ggplot(cData, 
       aes(x = total_counts, 
           y = total_counts_ERCC,
           col = batch)) + 
  geom_point()
```
